{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Corrections

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. In general, every single knot is equally spaced on the interval but inequally placing knots is needed when the input data is not equally observed. Additionally, at each $\tau_l$ the the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with single knot at each boundary. However, it is possible that placing multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure. A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

>>>>

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. In general, every single knot is equally spaced on the interval, but inequally placing knots is needed when the input data is not equally observed. Additionally, at each $\tau_l$, the polynomials on neighbouring subintervals must match derivatives up to order $m-2$ with a single knot at each boundary. However, it is sensible to place multiple coincident knots at some boundary when the functional data should not be differentiable due to the data structure. A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.
